# (APPENDIX) Appendices {-} 

# References {-}

<div id="refs"></div>


# Glossary

```{r, echo = FALSE}
glossary_table(link = FALSE)
```


# Licenses

* [Choosing between licenses](http://blog.psyarxiv.com/2018/05/14/licensing-work-psyarxiv/)
* [Creative Commons Licenses](https://creativecommons.org)
* [Open-source licenses](https://opensource.org/licenses) for code


# Repositories

(list under construction)

```{r, echo = FALSE}
library(dplyr)

repos <- tibble::tribble(
  ~name, ~link, ~doi, ~managed,
  "UK Data Service", "https://ukdataservice.ac.uk", F, T,
  "Open Science Framework (OSF)", "https://osf.io", T, F,
  "Harvard Dataverse", "https://dataverse.harvard.edu/", T, NA,
  "Databrary", "https://nyu.databrary.org/", T, T,
  "Figshare", "https://figshare.com/", T, F,
  "zenodo", "https://zenodo.org/", T, F,
  "GitHub", "https://github.com", F, F
) %>%
  mutate(service = glue::glue("<a href='{link}'>{name}</a>")) %>%
  select(service, doi, managed)

DT::datatable(repos, escape = FALSE)
```


## Registries

* [As Predicted](https://aspredicted.org/)
* [ClinicalTrials.gov](https://clinicaltrials.gov/)
* [Open Science Framework (OSF)](https://osf.io)
* [The American Economic Association's registry for randomized controlled trials](https://www.socialscienceregistry.org/)
* [EGAP Design Registration](https://egap.org/registry-0/)
* [Registry for International Development Impact Evaluations](http://ridie.3ieimpact.org/)
* [OSF Registered Report protocol registration](https://osf.io/rr/)

